Kindly Bent to Free Us

### 2020-05-20 kindly/motivation.tex
explanation added

The API for mutable linear arrays (\cref{sig:array})
aims to safely handle manual allocation and
deallocation of arrays that may contain affine elements.
A program would first use @create (n, v)@ to create
an array of size @n@ initialized with value
@v@. The value @v@ must be unrestricted as it is duplicated to
initialize all array elements. Using the @map@ function we
can transform the unrestricted elements into linear (affine)
ones. The resulting array can be processed further using @map@ (or @set@ if
affine). The @get@ function is only applicable if the element type
is unrestricted as one element is duplicated. The @length@
function is always applicable. To @free@ an array the elements must be
affine.

>>>>

The API for mutable linear arrays (\cref{sig:array})
aims to safely handle manual allocation and
deallocation of arrays that may contain affine elements.
A program would first use @create (n, v)@ to create
an array of size @n@ initialized with value
@v@. The value @v@ must be unrestricted as it is duplicated to
initialize all array elements. Using the @map@ and @map_copy@ functions we
can transform the unrestricted elements into linear (affine)
ones. The @map@ function consumes its input array, whereas @map_copy@
preserves the input. The implementation of @map@ \emph{might} perform
an in-place update, but this is neither required nor guaranteed. The
resulting array can be processed further using @map@ or 
@map_copy@ (or @set@ if affine). The @get@ function is only applicable
if the element type is unrestricted as one element is duplicated. The @length@
function is always applicable. To @free@ an array the elements must be
affine. An array with linear elements can only be freed by @map@ping
an explicit destructor over its elements.
